---
title       : Developing Data Products Presentation
subtitle    : States Data Comparison
author      : Khalid Ezzeldeen
job         : Student
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## States Data Comparison

This Application allows the user to compare between different USA states based on :

- Population
- Income
- Illiteracy
- Life Expectancy
- Number of Murders
- Frost
- Area

For more information about the data http://www.inside-r.org/r-doc/datasets/state.x77

---

## Uppload and pre-process data

Steps used to upload and refine the data

```{r}
library(datasets)
library(ggplot2)
library(shiny)
data(state)
statesData = as.data.frame(state.x77)
statesData$state = rownames(statesData)
statesData$state = as.factor(statesData$state)
statesData$LifeExp = statesData$"Life Exp"
head(statesData,1)
```

---

## Comprison Examples

Example 1 : Compare the population between New York, Washington, and California states 

```{r echo=TRUE,fig.width=10,fig.height=5}
ggplot(data=statesData[statesData$state %in% c("New York","Washington","California"),], 
       aes(x=state, y=Population)) + geom_bar(aes(fill=state),stat="identity")
```

---

## Comprison Examples (Continued)

Example 1 : Compare the area between different states 

```{r echo=TRUE,fig.width=10,fig.height=5}
ggplot(data=statesData[statesData$state %in% c("New York","Washington","California","Florida",
    "Colorado","Virginia"),],aes(x=state, y=Area)) + geom_bar(aes(fill=state),stat="identity")
```


